%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Zhuang (Tony) Tang} \\ \vspace{1pt}
    \small +61 466822796 $|$ \href{mailto:tonytang1199@gmail.com}{\underline{tonytang1199@gmail.com}} $|$ 
    \href{https://linkedin.com/in/zhuangtang}{\underline{linkedin.com/in/zhuangtang}} $|$
    \href{https://github.com/tonytang0909-grl}{\underline{github.com/tonytang0909-grl}}
    \href{https://tonytang0909-grl.github.io/Zhuangtang/}{\underline{https://tonytang0909-grl.github.io/Zhuangtang/}}
\end{center}
%-----------SUMMARY-----------
\section{SUMMARY}
Senior Backend \& Cloud Engineer with 10+ years of professional software engineering experience building distributed, cloud-native systems. Strong background in backend system design, event-driven architectures, and large-scale AWS integrations. Proven ability to lead complex technical initiatives, design reliable and observable services, and unblock teams through developer tooling and platform engineering. Experienced in CI/CD automation, enterprise systems, and applied machine learning, with growing exposure to AI/LLM-assisted development.


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages:} Java (primary), TypeScript(advanced), PHP(advanced), SQL; Python, JavaScript, C/C++ \\
    \textbf{Backend \& APIs:} Spring Boot, FastAPI, Flask, Node.js, REST, GraphQL, Webhooks \\
    \textbf{Cloud \& Distributed Systems:} AWS (Lambda, API Gateway, SQS, SNS, Step Functions), Event-driven systems, AWS CDK , Serverless\\
    \textbf{DevOps \& Reliability:} Docker, CI/CD (GitHub Actions, Jenkins, Bitbucket Pipelines), Monitoring \& Logging \\
    \textbf{Databases:} MySQL, PostgreSQL, MongoDB
  }}
\end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Adelaide}{Adelaide, South Australia}
      {Master of Computing and Innovation}{July. 2022 -- June 2024}
    \resumeSubheading
      {University College Dublin}{Dublin, Ireland}
      {Master of Computer Science}{July. 2012 -- Dec 2013}
    \resumeSubheading
      {Minzu University of China}{Beijing, China}
      {Bachelor of Electronic Engineer}{Sep. 2008 -- June 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Senior Software Developer}{Sep 2024 -- Present}
{Aligent Consulting Pty Ltd}{Adelaide, Australia}
\resumeItemListStart
  \resumeItem{Led and owned major Adobe Commerce (Magento 2) platform upgrades, including dependency alignment, extension compatibility analysis, migration planning, and production rollout.}
  \resumeItem{Designed and delivered highly customized enterprise e-commerce solutions integrating payments, logistics, ERP, CRM, and marketing platforms.}
  \resumeItem{Acted as technical lead for complex backend initiatives, owning system design, architectural decisions, and production readiness.}
  \resumeItem{Built distributed, event-driven cloud integrations using AWS Lambda, SQS, SNS, Step Functions, and AWS CDK.}
  \resumeItem{Defined integration standards, canonical schemas, and service contracts to reduce coupling and improve long-term maintainability.}
  \resumeItem{Led code reviews, mentored backend engineers, and drove improvements in developer productivity, reliability, and observability.}
\resumeItemListEnd


    \resumeSubheading
{Software Engineer}{Jan 2018 -- Apr 2022}
{AVIC Airport Runway Engineering Technology Co., Ltd}{Beijing, China}
\resumeItemListStart
  \resumeItem{Developed backend services using Spring Boot and relational databases to support internal and customer-facing platforms.}
  \resumeItem{Designed and implemented REST and GraphQL APIs to improve data access patterns and reduce over-fetching.}
  \resumeItem{Containerised services using Docker to ensure consistent deployment across environments.}
  \resumeItem{Built and maintained CI/CD pipelines with Jenkins and Docker, significantly reducing deployment time and manual errors.}
  \resumeItem{Collaborated with DevOps and product teams on system design, code reviews, and production support.}
\resumeItemListEnd

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
{Software Engineer / IT Systems Support}{Apr 2014 -- Jan 2018}
{Sino Engineering Pty Ltd}{China}
\resumeItemListStart
  \resumeItem{Maintained backend systems, servers, and internal applications supporting business operations.}
  \resumeItem{Designed and supported networked systems with a focus on reliability, security, and performance.}
  \resumeItem{Diagnosed and resolved system, network, and application issues across development and production environments.}
  \resumeItem{Authored technical documentation for system configurations and operational procedures.}
\resumeItemListEnd



  \resumeSubHeadingListEnd


%-----------Impacts-----------
\section{Key Impacts \& Strategic Initiatives}
\resumeItemListStart
  \resumeItem{Resolved a long-standing 4+ year local PWA debugging blocker by designing and delivering a Chrome-based debugging extension, unblocking frontend, backend, and DevOps teams and restoring local development capability.}
  \resumeItem{Designed and built a local AWS event capture and replay framework enabling Java-style step-through debugging for serverless workflows, eliminating risky live debugging and dramatically improving developer feedback loops.}
  \resumeItem{Led the redesign of the company’s integration platform, replacing tightly coupled Serverless/CDK monorepo workflows with a canonical schema–driven, composable pipeline architecture using adapters and customizable processing slots.}
  \resumeItem{Established integration standards and service contracts that significantly reduced coupling, improved extensibility, and accelerated onboarding of new enterprise integrations.}
  \resumeItem{Built a production-grade Adobe App Builder application replicating core Shopify Flow capabilities, positioning the company strategically as Adobe Commerce transitions away from traditional Magento extensibility.}
  \resumeItem{Designed and delivered a fully functional, commercialized BigCommerce application using Gadget.dev, providing Shopify-equivalent automation and workflow capabilities and opening a new revenue stream.}
\resumeItemListEnd




%-----------AWARDS-----------
\section{AWARDS}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{30\% Global Citizens Scholarship} $|$ \emph{The University of Adelaide}}{2023}
        \resumeProjectHeading
            {\textbf{15\% Global Citizens Scholarship} $|$ \emph{The University of Adelaide}}{2022}
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
